Viral Sequence Sorting Evaluation

### 2022-08-10 EnvironmentalData/EarlyIterations/identifying_viral_contigs_20220521.Rmd
Updated directory structure.

```{r}
comp_pipelines <- tibble(pipeline="example", precision=0, recall=0, F1=0)
```

@@

```{r}
ggplot(confusion_by_taxa, aes(x=count, y=seqtype,
                   fill=confusion_matrix,
                   color=confusion_matrix)) +
  geom_bar(stat="identity") +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(4)), 0.5),
                    labels=c("false negative", "false positive", 
                             "true negative", "true positive")) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(4)), 1),
                    labels=c("false negative", "false positive", 
                             "true negative", "true positive")) +
  xlab("Number of Sequences") +
  ylab("") 
```

# Using NMDS to compare the tools
get matrix want to use for beta diversity
```{r}
virus_score_matrix <- viruses %>% select(keep_score_vb, keep_score_dvf,keep_score_vs2, keep_score_cv, keep_score_vb_cv, keep_score_dvf_cv,keep_score_vs2_cv, keep_score_cv_kj, keep_score_all)

@@

>>>>

@@

p2 <- ggplot(confusion_by_taxa, aes(x=count, y=seqtype,
                   fill=confusion_matrix,
                   color=confusion_matrix)) +
  geom_bar(stat="identity") +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(4)), 0.5),
                    labels=c("false negative", "false positive", 
                             "true negative", "true positive")) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(4)), 1),
                    labels=c("false negative", "false positive", 
                             "true negative", "true positive")) +
  xlab("Number of Sequences") +
  ylab("")

p2
```

```{r}
png("testing_set_accuracy_by_taxa.png", width=6.8, height=3.2, units="in", res=400)

p2

dev.off()
```

# Visualizing confusion matrix by number of tools

```{r}
viruses$confusion_matrix <- "true positive"
viruses$confusion_matrix[viruses$seqtype=="virus" & viruses$keep_score_all<1] <- "false negative"
viruses$confusion_matrix[viruses$seqtype!="virus" & viruses$keep_score_all>=1] <- "false positive"
viruses$confusion_matrix[viruses$seqtype!="virus" & viruses$keep_score_all<1] <- "true negative"

viruses$keep_score_visualize <- viruses$keep_score_all
viruses$keep_score_visualize[viruses$keep_score_all>1] <- ">1"

viruses$keep_score_visualize <- factor(viruses$keep_score_visualize, 
                                       levels=c("-0.5", "-1", "0", "0.5","1", ">1"))
viruses$keep_score_visualize <- factor(viruses$keep_score_visualize, 
                                       labels=c("≤ 0", "≤ 0", "≤ 0", "0.5","1", "> 1"))
```

```{r}
levels(factor(viruses$keep_score_visualize))
```

p1 <- ggplot(viruses, aes(x=confusion_matrix,
                   fill=keep_score_visualize, color=keep_score_visualize)) +
  geom_bar(stat="count", position="stack") +
  theme_light() +
  coord_flip() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16)
  ) +
  scale_color_manual(name = 'Viral Score',
                     values = alpha(c(pal(4)), 1)) +
  scale_fill_manual(name = 'Viral Score',
                     values = alpha(c(pal(4)), 0.5)) +
  xlab("") +
  ylab("Sequence Count")

p1
```

```{r}
png("testing_set_accuracy_confusion_matrix.png", width=6.8, height=2.6, units="in", res=400)

p1

dev.off()
```

# Using NMDS to compare the tools
get matrix want to use for beta diversity
```{r}
virus_score_matrix <- viruses %>% select(keep_score_vb, keep_score_dvf,keep_score_vs2, keep_score_cv, keep_score_vb_cv, keep_score_dvf_cv,keep_score_vs2_cv, keep_score_kj_cv, keep_score_all)

@@

# Correlating Scores and Other parameters

```{r}
cor(viruses$keep_score_all, viruses$hallmark, method="pearson")
```

```{r}
cor(viruses$keep_score_all, viruses$percent_unknown, method="pearson")
```

```{r}
cor(viruses$keep_score_all, viruses$percent_viral, method="pearson")
```
